---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rscrapss

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/stephaniereinders/rscrapps/branch/master/graph/badge.svg)](https://codecov.io/gh/stephaniereinders/rscrapps?branch=master)
[![Travis build status](https://travis-ci.com/stephaniereinders/rscrapps.svg?branch=master)](https://travis-ci.com/stephaniereinders/rscrapps)
<!-- badges: end -->

The main purpose of rscrapps is to allow a user to easily search the Google Play Store for apps and scrape information from those apps' pages.

## Installation

<!-- You can install the released version of rscrapps from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("rscrapps") -->
<!-- ``` -->

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stephaniereinders/rscrapps")
```

## Example

Suppose you want to gather information on steganography apps listed on the Google Play Store. You can run the function getDataForApps with inputs search_term = "steganography" and num_apps = 5. The function will first search the Google Play Store for apps using steganography as the search term. Then the function will scrape the Google Play Store pages of the first 5 apps listed in the search results. If you want to scrape the app pages of all of the apps in the search results, you can run the function with num_apps = "all" but be forwarned that the function can take a while to run depending on the number of apps in the search results.  

```{r example}
library(rscrapps)

data <- getDataForApps(search_term = "steganography", num_apps =  5)

data

```

If you want to scrape the Google Play Store app page of a specific app, you can use the function getDataForSingleApp. The input is the url to the app's page on the Google Play Store.

```{r}
data <- getDataForSingleApp("https://play.google.com/store/apps/details?id=com.hulu.plus")

data
```




