---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rscrapss

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/stephaniereinders/rscrapps/branch/master/graph/badge.svg)](https://codecov.io/gh/stephaniereinders/rscrapps?branch=master)
[![Travis build status](https://travis-ci.com/stephaniereinders/rscrapps.svg?branch=master)](https://travis-ci.com/stephaniereinders/rscrapps)
<!-- badges: end -->

The main purpose of rscrapps is to allow a user to easily search the Google Play Store for apps and scrape information from those apps' pages.

## Installation

<!-- You can install the released version of rscrapps from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("rscrapps") -->
<!-- ``` -->

You can install the development version from [GitHub](https://github.com/) with:

``` r
install.packages("devtools")
devtools::install_github("stephaniereinders/rscrapps")
```

## Example 1: Search for apps and scrape their Google Play Store pages 

The function getDataForApps will search the Google Play Store for apps using the input search_term and scrape data from those apps' Google Play Store pages. The function also allows you to specify the number of apps to scrape using the input num_apps. To scrape all of the apps listed in the search results, use num_apps = "all". 

```{r example}
library(rscrapps)

getDataForApps(search_term = "steganography", num_apps =  5)
```

## Example 2: Scrape the Google Play Store page of a single app

If you want to scrape the Google Play Store app page of a specific app, you can use the function getDataForSingleApp. The input is the url to the app's page on the Google Play Store.

```{r}
getDataForSingleApp("https://play.google.com/store/apps/details?id=com.hulu.plus")
```



